Learning Network Size while Training with ShrinkNets

### 2018-02-05 paper/ICML/theory.tex

>>>>

\begin{itemize}
  \item Comparison to group sparsity
  \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
  \item We conclude that without this constraint our formulation has more degree of freedom
  \item What happen when we drop this constraint
  \item The problem becomes non-convex and without a global minimum
  \item Not having a global minimum is bad, how can we solve that ?
  \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
\end{itemize}
